Supporting information: Copulas and their potential for ecology

### 2019-10-01 SupportingInformation.Rmd
finished editing (for now) the Q1 sections, but Shyanolina needs to fix a couple things
comments in prep for revisions for the Q2 sections#

@@

<!--Now the copula figures that were not presented in the main text-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=7.5in]{./Results/PedagogSuppMat_SurvClayton.pdf}
\caption[Example survival Clayton copulas]{Log-transformed pdfs (A-E) and samples (F-J) 
from example survival Clayton 
copulas. K is Kendall correlation; p is the value of the parameter for the survival Clayton 
family (it is a one-parameter family); and LT and UT are the measures of lower- and 
upper-tail dependence, respectively. The parameter range for the family is $p \in (0,\infty)$, upper-tail dependence is $2^{-1/p}$ and lower-tail
dependence is $0$.\label{figped_SC}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=7.5in]{./Results/PedagogSuppMat_Gumbel.pdf}
\caption[Example Gumbel copulas]{Log-transformed pdfs (A-E) and samples (F-J) from example Gumbel copulas. K is Kendall 
correlation; $p$ is the value of the parameter for the Gumbel family (it is a 
one-parameter family); and LT and UT are the measures of lower- and upper-tail dependence, 
respectively. The parameter range for the family is $p \in [1,\infty)$, lower-tail dependence is $0$ and upper-tail
dependence is $2-2^{1/p}$.\label{figped_G}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=7.5in]{./Results/PedagogSuppMat_Joe.pdf}
\caption[Example J copulas]{Log-transformed pdfs (A-E) and samples (F-J) from example J copulas. K is Kendall correlation; $p$ is the value of the parameter for the J family (it is a 
one-parameter family); and LT and UT are the measures of lower- and upper-tail dependence, 
respectively. The parameter range for the family is $p \in [1,\infty)$, lower-tail dependence is $0$ and upper-tail
dependence is $2-2^{1/p}$.\label{figped_J}}
\end{center}
\end{figure}

@@

<!--Plots for AR(1) with Gumbel-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_D2u-D2l_vs_Kendall's Tau.pdf}\\
\hspace{-0.8cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[Comparison of copula structure of noise and model output, AR(1) model, 
Gumbelcopula.]{Comparison of copula structure of noise inputs and model outputs, AR(1) 
model, Gumbelcopula. Same format as Figs \ref{fig_Cause4copula_C_kend_ar1} and 
\ref{MT-fig_Cause4copula_scatter_C_kend_ar1}, see captions of those figures for 
details.\label{fig_Cause4copula_G_kend_ar1}}
\end{center}
\end{figure}

@@

<!--Plots for AR(1) with Joe-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_D2u-D2l_vs_Kendall's Tau.pdf}\\
\hspace{-0.8cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[Comparison of copula structure of noise and model output, AR(1) model, 
J copula.]{Comparison of copula structure of noise inputs and model outputs, AR(1) 
model, J copula. Same format as Figs \ref{fig_Cause4copula_C_kend_ar1} and 
\ref{MT-fig_Cause4copula_scatter_C_kend_ar1}, see captions of those figures for 
details.\label{fig_Cause4copula_J_kend_ar1}}
\end{center}
\end{figure}

@@

<!--Plots for stochastic ricker with weak noise (Joe copula) : nsd=0.1-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_D2u-D2l_vs_Kendall's Tau.pdf}\\
\hspace{-0.8cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[Comparison of copula structure of noise and model output, stochastic Ricker 
model, weak noise, J copula.]{Comparison of copula structure of noise inputs and model 
outputs, stochastic Ricker model, weak noise, J copula. Same format as Figs 
\ref{fig_Cause4copula_C_kend_ar1} and \ref{MT-fig_Cause4copula_scatter_C_kend_ar1}, 
see captions of those figures for details.\label{fig_Cause4copula_J_kend_sRicker_nsd_0.1}}
\end{center}
\end{figure}

>>>>

<!--survival clayton copula-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=7.5in]{./Results/PedagogSuppMat_SurvClayton.pdf}
\caption[Example survival Clayton copulas]{Log-transformed pdfs (A-E) and samples (F-J) 
from example survival Clayton 
copulas. K is Kendall correlation; p is the value of the parameter for the survival Clayton 
family (it is a one-parameter family); and LT and UT are the measures of lower- and 
upper-tail dependence, respectively. The parameter range for the family is $p \in (0,\infty)$, upper-tail dependence is $2^{-1/p}$ and lower-tail
dependence is $0$.\label{figped_SC}}
\end{center}
\end{figure}

@@

<!--Now the copula figures that were not presented in the main text-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=7.5in]{./Results/PedagogSuppMat_Gumbel.pdf}
\caption[Example Gumbel copulas]{Log-transformed pdfs (A-E) and samples (F-J) from example Gumbel copulas. K is Kendall 
correlation; $p$ is the value of the parameter for the Gumbel family (it is a 
one-parameter family); and LT and UT are the measures of lower- and upper-tail dependence, 
respectively. The parameter range for the family is $p \in [1,\infty)$, lower-tail dependence is $0$ and upper-tail
dependence is $2-2^{1/p}$.\label{figped_G}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=7.5in]{./Results/PedagogSuppMat_Joe.pdf}
\caption[Example Joe copulas]{Log-transformed pdfs (A-E) and samples (F-J) from example Joe copulas. K is Kendall correlation; $p$ is the value of the parameter for the Joe family (it is a 
one-parameter family); and LT and UT are the measures of lower- and upper-tail dependence, 
respectively. The parameter range for the family is $p \in [1,\infty)$, lower-tail dependence is $0$ and upper-tail
dependence is $2-2^{1/p}$.\label{figped_J}}
\end{center}
\end{figure}

@@

<!--Plots for AR(1) with Gumbel-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_D2u-D2l_vs_Kendall's Tau.pdf}\\
\hspace{-0.8cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[Comparison of copula structure of noise and model output, AR(1) model, 
Gumbel copula.]{Comparison of copula structure of noise inputs and model outputs, AR(1) 
model, Gumbelcopula. Same format as Figs \ref{fig_Cause4copula_C_kend_ar1} and 
\ref{MT-fig_Cause4copula_scatter_C_kend_ar1}, see captions of those figures for 
details.\label{fig_Cause4copula_G_kend_ar1}}
\end{center}
\end{figure}

@@

<!--Plots for AR(1) with Joe-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_D2u-D2l_vs_Kendall's Tau.pdf}\\
\hspace{-0.8cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Joe/Joe_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[Comparison of copula structure of noise and model output, AR(1) model, 
Joe copula.]{Comparison of copula structure of noise inputs and model outputs, AR(1) 
model, Joe copula. Same format as Figs \ref{fig_Cause4copula_C_kend_ar1} and 
\ref{MT-fig_Cause4copula_scatter_C_kend_ar1}, see captions of those figures for 
details.\label{fig_Cause4copula_J_kend_ar1}}
\end{center}
\end{figure}

@@

<!--Plots for stochastic ricker with weak noise (Joe copula) : nsd=0.1-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_D2u-D2l_vs_Kendall's Tau.pdf}\\
\hspace{-0.8cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_0.1_r_0.5_K_100_Joe/Joe_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[Comparison of copula structure of noise and model output, stochastic Ricker 
model, weak noise, Joe copula.]{Comparison of copula structure of noise inputs and model 
outputs, stochastic Ricker model, weak noise, Joe copula. Same format as Figs 
\ref{fig_Cause4copula_C_kend_ar1} and \ref{MT-fig_Cause4copula_scatter_C_kend_ar1}, 
see captions of those figures for details.\label{fig_Cause4copula_J_kend_sRicker_nsd_0.1}}
\end{center}
\end{figure}

<!--Plots for stochastic ricker with strong noise (Joe copula) : nsd=1-->
\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_1_r_0.5_K_100_Joe/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_1_r_0.5_K_100_Joe/Joe_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_1_r_0.5_K_100_Joe/Joe_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_1_r_0.5_K_100_Joe/Joe_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_1_r_0.5_K_100_Joe/Joe_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_1_r_0.5_K_100_Joe/Joe_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_1_r_0.5_K_100_Joe/Joe_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_1_r_0.5_K_100_Joe/Joe_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_1_r_0.5_K_100_Joe/Joe_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_1_r_0.5_K_100_Joe/Joe_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_1_r_0.5_K_100_Joe/Joe_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_1_r_0.5_K_100_Joe/Joe_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_1_r_0.5_K_100_Joe/Joe_D2u-D2l_vs_Kendall's Tau.pdf}\\
\hspace{-0.8cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_1_r_0.5_K_100_Joe/Joe_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_1_r_0.5_K_100_Joe/Joe_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ricker_nsd_1_r_0.5_K_100_Joe/Joe_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[Comparison of copula structure of noise and model output, stochastic Ricker 
model, strong noise, Joe copula.]{Comparison of copula structure of noise inputs and model 
outputs, stochastic Ricker model, strong noise, Joe copula. Same format as Figs 
\ref{fig_Cause4copula_C_kend_ar1} and \ref{MT-fig_Cause4copula_scatter_C_kend_ar1}, 
see captions of those figures for details.\label{fig_Cause4copula_J_kend_sRicker_nsd_1}}
\end{center}
\end{figure}
